Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-03-07 paper.tex
Address John's comments on budget comtributions time series on page 9. Removed crossed-out words.

Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq. \ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in subsaturated environments.
The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:n2dry} throughout the entire domain.
Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
The right column depicts the residuals, computed using Eq. \ref{eq:residual} (i.e. the left column minus the center column.)
In every 24-hour period, the budget changes are nearly identical to the model changes, which is reflected in the near-zero residuals in the right column.
This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the anaysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget tendencies in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.

In the tropopause layer, some of the budget terms are small enough to be ignored.
To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq. \ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.~\ref{fig:avgbudterms}.
For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain. 
Thus, taking an average over the domain tends to wash out the positive and negative contributions.
To circumvent this problem, the absolute value of each of the terms is averaged.}. 
Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
The remaining three processes - horizontal turbulence, microphysics, and dissipative heating - lie atop one another near zero.
Although the horizontal turbulence and microphysics terms can be quite large in the eyewall region, they are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
Dissipative heating, meanwhile, is relatively small everywhere.
%Although the contribution from horizontal turbulence (Fig.~\ref{fig:avgbudterms}, purple line) becomes more important after 48 hours, it is confined to a very small region immediately surrounding the eyewall tangential velocity maximum (not shown), and is negligible throughout the rest of the tropopause layer.
%The two remaining processes - microphysics and dissipative heating (Fig.~\ref{fig:avgbudterms}, orange and light green lines, respectively) - lie atop one another near zero.
%Although the latent heating term can be quite large in the eyewall region, it is negligible everywhere outside of the eyewall, as are the effects of dissipative heating.

>>>>

Eqs. \ref{eq:budgetchange}-\ref{eq:residual} are plotted for three consecutive 24-hour periods in Fig.~\ref{fig:mod+bud+res}.
For this and all subsequent radial-vertical cross sections, a 1-2-1 smoother is applied once in the radial direction to eliminate $2\Delta r$ noise that appears in some of the raw model output and calculated fields.
      The left column of Fig.~\ref{fig:mod+bud+res} depicts the model changes computed using Eq. \ref{eq:modelchange}, together with Eq.~\ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in subsaturated environments.
The center column depicts the budget changes computed using Eq. \ref{eq:budgetchange} together with Eq.~\ref{eq:n2dry} throughout the entire domain.
Thus, the left column includes the effect of moisture in the $N^2$ computations, whereas the center column neglects moisture.
The right column depicts the residuals, computed using Eq. \ref{eq:residual} (i.e. the left column minus the center column.)
In every 24-hour period, the budget changes are nearly identical to the model changes, which is reflected in the near-zero residuals in the right column.
This indicates that the budget accurately represents the model variability, which implies that the neglect of moisture in the budget computation introduces negligible error within the analysis domain\footnote{This is not the case in the lower- and mid-troposphere, where the residual actually exceeds the budget tendencies in many places, likely due to the neglect of moisture; thus we limit this analysis to the upper troposphere and lower stratosphere.}.

In the tropopause layer, some of the budget terms are small enough to be ignored.
To determine which of the budget terms are most important, a time series of the contribution of each of the budget terms in Eq. \ref{eq:dthetadt} to the tropopause-layer static stability tendency is plotted in Fig.~\ref{fig:avgbudterms}.
For this figure, each of the budget terms is computed using the method described in Section 3, except with 1-hour averaging intervals instead of 24-hour intervals.
The absolute values of these tendencies are then averaged over the radius-height domain of the plots shown in Fig.~\ref{fig:mod+bud+res} and plotted as a time series\footnote{It will be seeen in subsequent figures that each of the terms contributes both positively and negatively to the $N^2$ tendency within the analysis domain. 
Thus, taking an average over the domain tends to wash out the positive and negative contributions.
To circumvent this problem, the absolute value of each of the terms is averaged.}. 
Advection (Fig.~\ref{fig:avgbudterms}, red line) plays an important role in the mean tropopause-layer static stability tendency at all times, and vertical turbulence (Fig.~\ref{fig:avgbudterms}, blue line) and radiation (Fig.~\ref{fig:avgbudterms}, dark green line) also contribute significantly.
The remaining three processes - horizontal turbulence, microphysics, and dissipative heating -  are negligible everywhere outside of the eyewall, and do not play important roles in the mesoscale tropopause variability.
